### 2023-11-03 Scripts/Manuscript/manuscript.Rmd
added code to load in the retrieved ML data to soon be able to store the data.

This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and XXX data are available at <https://github.com/CasGoos/WORCSPersonalTemplate.git>.

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(31102023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

Data collection, coding protocol, and planned analyses were all preregistered. The preregistration and supplementary materials can be found on this thesis' OSF page: <https://osf.io/9r8yt/>. Any deviations from the preregistration are explicitly mentioned in the text.

>>>>

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

Data collection, coding protocol, and planned analyses were all preregistered. The preregistration and supplementary materials can be found on this thesis' OSF page: <https://osf.io/9r8yt/>. Any deviations from the preregistration are explicitly mentioned in the text. This manuscript was generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and XXX data are available at <https://github.com/CasGoos/measurement_and_replication.git>.
